CMPEN/EE 454 Project 2 Report

### 2015-12-12 p2/report/project_report.tex
more to report, cleaned up code sections

\lstset{ %
	language=C,
	basicstyle=\ttfamily\footnotesize,
	keywordstyle=\ttfamily\color{blue}\footnotesize,
	commentstyle=\color{OliveGreen}\ttfamily\footnotesize,
	texcl,
	escapechar =`
	escapebegin=\lst@commentstyle,
	showspaces=false,
	showtabs=false,
	numbers=left,
	showstringspaces=false,
	frame=single
}
\makeatother

@@

\newpage
\pagenumbering{arabic}
\setcounter{page}{1}
\section{Integral Algorithms}
\subsection{Harris Corner Detection}
\subsubsection{Synopsis}
Harris corner detection is an algorithm which detect corners in images that can be used to create point correspondences between time series images.  A ``corner'' can loosely be defined as a feature in the image located at coordinates $(x_0,y_0)$ such that $\frac{\partial I}{\partial x}(x_0,y_0)$ and $\frac{\partial I}{\partial y}(x_0,y_0)$ yield relatively large values.
\subsubsection{Implementation}
Below the implementation of the Harris corner detection algorithm in C-like pseudocode.
\begin{lstlisting}

@@

\end{lstlisting}
This routine returns a non-normalized intensity image where strong intensities correspond to corner points in the image patch.  Once this intensity image has been computed, it is passed to a thresholding routine where the coordinate points of these corners is determined.

\begin{minipage}{\textwidth}
\begin{lstlisting}

@@

assignment_set compute_bb_set(bounding_box a,b) {

	// Compute the costs of corresponding each corner
	// point in bounding box a against every corner
	// point in bounding box b.
	for (corner_a : a) {
	for (corner_b : b) {
		// Get the image patches around each corner point.
		patch_a = get_patch(corner_a);
		patch_b = get_patch(corner_b);

@@

assignment_set compute_img_set(image a,b) {

	// Compute the costs of corresponding each bounding box
	// in image a against every bounding box in image b.
	for (bounding_box_a : a) {
	for (bounding_box_b : b) {

@@

\end{lstlisting}
\end{minipage}
\subsection{RANSAC}

>>>>

\lstset{ %
	language=C,
	basicstyle=\ttfamily\footnotesize,
	keywordstyle=\ttfamily\color{blue}\footnotesize,
	commentstyle=\color{OliveGreen}\ttfamily\footnotesize,
	texcl,
	escapechar =`
	escapebegin=\lst@commentstyle,
	showspaces=false,
	showtabs=false,
	numbers=left,
	showstringspaces=false,
	frame=single,
	tabsize=3
}
\makeatother

@@

\newpage
\pagenumbering{arabic}
\setcounter{page}{1}
\section{Project Summary}
The purpose of this project was to perform object tracking in a time-series image set using many of the different image processing learned in class.

\section{Integral Algorithms}
\subsection{Harris Corner Detection}
\subsubsection{Synopsis}
Harris corner detection is an algorithm which detect corners in images that can be used to create point correspondences between time series images.  A ``corner'' can loosely be defined as a feature in the image located at coordinates $(x_0,y_0)$ such that $\frac{\partial I}{\partial x}(x_0,y_0)$ and $\frac{\partial I}{\partial y}(x_0,y_0)$ yield relatively large values.
\subsubsection{Implementation}
Below the implementation of the Harris corner detection algorithm in C-like pseudocode.
\\~\\
\begin{minipage}{\textwidth}
\begin{lstlisting}

@@

This routine returns a non-normalized intensity image where strong intensities correspond to corner points in the image patch.  Once this intensity image has been computed, it is passed to a thresholding routine where the coordinate points of these corners is determined.
\\~\\
\begin{minipage}{\textwidth}
\begin{lstlisting}

@@

assignment_set compute_bb_set(bounding_box_a, bounding_box_b) {

	// Compute the costs of corresponding each corner
	// point in bounding box a against every corner
	// point in bounding box b.
	for (corner_a : bounding_box_a) {
	for (corner_b : bounding_box_b) {
		// Get the image patches around each corner point.
		patch_a = get_patch(corner_a);
		patch_b = get_patch(corner_b);

@@

assignment_set compute_img_set(image_a, image_b) {

	// Compute the costs of corresponding each bounding box
	// in image a against every bounding box in image b.
	for (bounding_box_a : image_a) {
	for (bounding_box_b : image_b) {

@@

\end{lstlisting}
\end{minipage}
\newpage
\subsection{RANSAC}
\subsubsection{Synopsis}
Once the optimal bounding box correspondences have been determined, random sample consensus (RANSAC) can be used to estimate the translation of a bounding box between two images.  RANSAC is a probabilistic, consensus-based algorithm which can be used to efficiently remove outliers from a set - in this problem space, outliers are ``bad'' corner points correspondences determined by the \texttt{compute\_bb\_set} function.
\subsubsection{Implementation}
\begin{minipage}{\textwidth}
\begin{lstlisting}

estimated_translation ransac(bounding_box_i, bounding_box_j,
	num_iterations, threshold) {

// Perform the inner-routine num\_iteartion times.
for (i = 1 to num_iterations) {
	// Get a random pair of corresponding corners
	// from the bounding boxes.
	corner_i = get_random_corner(bounding_box_i);
	corner_j =
	get_corresponding_corner(bounding_box_j, corner_i);

	// Get the component-wise translation between these
	// corresponding points.
	translation = compute_translation(corner_i, corner_j);

	inlier_count = 0;
	max_inlier_count = 0, best_translation = 0;

	for (corner : bounding_box_i) {
		// Estimate where all the other corners should be based
		// on the translation computed above.
		estimated_corner = corner + translation;

		// Get the actual correspondence point
		actual_corner =
			get_corresponding_corner(bounding_box_j, corner);

		// If the estimated point is close to the actual point,
		// consider the point an inlier.
		distance = l2norm(actual_corner, estimated_corner);
		if (distance < threshold) inlier_count++;
	}

	// Keep track of the best translation estimate.
	if (inlier_count > max_inlier_count) {
		max_inlier_count = inlier_count;
		best_translation = translation;
	}

} return best_translation; }
